Fast, Scalable Phrase-Based SMT Decoding

### 2016-10-18 amta.2016/acl2016.tex
move to amta.2016
spelt nikolay name wrong

\author{Hieu Hoang\\
	    Moses Machine Translation CIC\\
	    {\tt hieu@moses-mt.org}
	  \And
	Nicolay Bogoychev\\
  	University of Edinburgh\\
  	10 Crichton Street\\
  	Edinburgh, Scotland, EH10 9AB\\
  {\tt s1031254@sms.ed.ac.uk}
	  \And
	Lane Schwartz\\
  	University of Illinois\\
  {\tt lanes@illinois.edu}
	  \AND
	Kenneth Heafield\\
  	University of Edinburgh\\
  {\tt kheafiel@inf.ed.ac.uk}
	  \And
	Marcin Junczys-Dowmunt\\
	Faculty of Mathematics and Computer Science \\
	Adam Mickiewicz University\\
  {\tt junczys@amu.edu.pl}
	}

@@

As a baseline, we use a recent\footnote{The experiments were performed between January and May 2016 with the latest github code to hand. The main ar-en experiments were rerun with the source code as at 8th June, 2016 to ensure there were no material difference. The commit hash was \scriptsize{bc5f8d15c6ce4bc678ba992860bfd4be6719cee8} } version of the Moses decoder taken from the github repository.

>>>>

\author{Hieu Hoang\\
	    Moses Machine Translation CIC\\
	    {\tt hieu@moses-mt.org}
	  \And
	Nikolay Bogoychev\\
  	University of Edinburgh\\
  	10 Crichton Street\\
  	Edinburgh, Scotland, EH10 9AB\\
  {\tt s1031254@sms.ed.ac.uk}
	  \And
	Lane Schwartz\\
  	University of Illinois\\
  {\tt lanes@illinois.edu}
	  \AND
	Kenneth Heafield\\
  	University of Edinburgh\\
  {\tt kheafiel@inf.ed.ac.uk}
	  \And
	Marcin Junczys-Dowmunt\\
	Faculty of Mathematics and Computer Science \\
	Adam Mickiewicz University\\
  {\tt junczys@amu.edu.pl}
	}

@@

As a baseline, we use a recent\footnote{The experiments were performed between January and May 2016 with the latest github code to hand. The main ar-en experiments were rerun with the source code as of 8th June, 2016 to ensure there were no material difference. The commit hash was \scriptsize{bc5f8d15c6ce4bc678ba992860bfd4be6719cee8} } version of the Moses decoder taken from the github repository.
